Introducing ICBe: Supplementary Information

### 2022-09-21 replication_paper/political_analysis_draft/appendix.tex
all the fixes

\usepackage[utf8]{inputenc}
\usepackage{pifont}
\usepackage{newunicodechar}
\newunicodechar{✓}{\ding{51}}
\newunicodechar{✗}{\ding{55}}
\usepackage{array}
\usepackage{ctable}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{titlesec}
\usepackage[parfill]{parskip}
\usepackage{makecell}
\usepackage{graphicx}
\usepackage{rotating}
\usepackage{float}
\usepackage{setspace}
\usepackage{cellspace}
\setlength\cellspacetoplimit{0.8ex}
\renewcommand{\arraystretch}{0.8}
\AtBeginEnvironment{lltable}{\singlespacing}
\usepackage{subcaption}
\usepackage{atbegshi}% http://ctan.org/pkg/atbegshi
\usepackage{float}
\usepackage{algorithm2e}
\usepackage{amsmath}
\usepackage{changepage}
\renewenvironment{abstract}{}{}
\usepackage{adjustbox}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{colortbl}
\usepackage{hhline}
\usepackage{longtable}
\usepackage{array}
\usepackage{hyperref}
\begin{document}
\maketitle

@@

\hypertarget{appendix-a-corpus-and-cases}{%
\section{Appendix A Corpus and
Cases}\label{appendix-a-corpus-and-cases}}

\hypertarget{app:crises}{%
\subsection{Table A1: ICBe Crises and Summary
Information}\label{app:crises}}

@@

\hypertarget{app:verbs}{%
\subsection{Table A2: Verb Meanings (Glosses) found in the ICB Corpus
(top 200)}\label{app:verbs}}

@@

\hypertarget{appendix-b-coding-process}{%
\section{Appendix B: Coding Process}\label{appendix-b-coding-process}}

@@

\hypertarget{app:gui}{%
\subsection{Figure B1: Graphical User Interface}\label{app:gui}}

@@

\hypertarget{app:algo1}{%
\subsection{Algorithm B2: Coding Aggregation and
Filtering}\label{app:algo1}}

@@

\hypertarget{app:intercoderagreement}{%
\subsection{Figure B3 : Intercoder
Agreement}\label{app:intercoderagreement}}

@@

\hypertarget{app:agreement_by_confidence}{%
\subsection{Figure B4 : Intercoder Agreement by
Confidence}\label{app:agreement_by_confidence}}

@@

\hypertarget{appendix-c-recall}{%
\section{Appendix C: Recall}\label{appendix-c-recall}}

@@

\hypertarget{algorithm-c1-synthetic-narratives}{%
\subsection{Algorithm C1: Synthetic
Narratives}\label{algorithm-c1-synthetic-narratives}}

@@

\hypertarget{table-c2-synthetic-narrative-matches-cuban-missile}{%
\subsection{Table C2: Synthetic Narrative Matches Cuban
Missile}\label{table-c2-synthetic-narrative-matches-cuban-missile}}

@@

\hypertarget{table-c3-synthetic-narrative-matches-crimea-donbas}{%
\subsection{Table C3: Synthetic Narrative Matches
Crimea-Donbas}\label{table-c3-synthetic-narrative-matches-crimea-donbas}}

@@

\hypertarget{appendix-d-precision}{%
\section{Appendix D: Precision}\label{appendix-d-precision}}

\hypertarget{figure-d1-crimea-donbas}{%
\subsection{Figure D1 Crimea-Donbas}\label{figure-d1-crimea-donbas}}

@@

\hypertarget{table-d2-stratified-sentence-examples}{%
\subsection{Table D2: Stratified Sentence
Examples}\label{table-d2-stratified-sentence-examples}}

@@

\hphantom{em}
\begin{figure}[H]
\centering{\includegraphics[height=21cm]{"./ft_sample_precision_precision4.png"}}
\end{figure}
\clearpage

\hypertarget{figure-d3-crisis-maps-cuban-missiles}{%
\subsection{Figure D3 Crisis Maps Cuban
Missiles}\label{figure-d3-crisis-maps-cuban-missiles}}

@@

\hypertarget{figure-d4-crisis-maps-crimea-donbas}{%
\subsection{Figure D4 Crisis Maps
Crimea-Donbas}\label{figure-d4-crisis-maps-crimea-donbas}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-reimersSentenceBERTSentenceEmbeddings2019}{}}%
Reimers, Nils, and Iryna Gurevych. 2019. {``Sentence-{BERT}: {Sentence
Embeddings} Using {Siamese BERT-Networks}.''}
\url{http://arxiv.org/abs/1908.10084}.

\leavevmode\vadjust pre{\hypertarget{ref-reimersMakingMonolingualSentence2020}{}}%
---------. 2020. {``Making {Monolingual Sentence Embeddings
Multilingual} Using {Knowledge Distillation}.''}
\url{http://arxiv.org/abs/2004.09813}.

\leavevmode\vadjust pre{\hypertarget{ref-shleiferPretrainedSummarizationDistillation2020}{}}%
Shleifer, Sam, and Alexander M. Rush. 2020. {``Pre-Trained
{Summarization Distillation}.''} \url{http://arxiv.org/abs/2010.13002}.

>>>>

\usepackage[utf8]{inputenc}
\usepackage{pifont}
\usepackage{newunicodechar}
\newunicodechar{✓}{\ding{51}}
\newunicodechar{✗}{\ding{55}}
\usepackage{array}
\usepackage{ctable}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{titlesec}
\usepackage[parfill]{parskip}
\usepackage{makecell}
\usepackage{graphicx}
\usepackage{rotating}
\usepackage{float}
\usepackage{setspace}
\usepackage{cellspace}
\setlength\cellspacetoplimit{0.8ex}
\renewcommand{\arraystretch}{0.8}
\AtBeginEnvironment{lltable}{\singlespacing}
\usepackage{subcaption}
\captionsetup[algorithm]{labelformat=empty}
\captionsetup[figure]{labelformat=empty}
\usepackage{atbegshi}% http://ctan.org/pkg/atbegshi
\usepackage{float}
\usepackage{algorithm2e}
\usepackage{amsmath}
\usepackage{changepage}
\renewenvironment{abstract}{}{}
\usepackage{adjustbox}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{colortbl}
\usepackage{hhline}
\usepackage{longtable}
\usepackage{array}
\usepackage{hyperref}
\begin{document}
\maketitle

@@

\hypertarget{corpus-and-cases}{%
\section{Corpus and Cases}\label{corpus-and-cases}}

\hypertarget{app:crises}{%
\subsection{ICBe Crises and Summary Information}\label{app:crises}}

@@

\hypertarget{app:verbs}{%
\subsection{Verb Meanings (Glosses) found in the ICB Corpus (top
200)}\label{app:verbs}}

@@

\hypertarget{coding-process}{%
\section{Coding Process}\label{coding-process}}

@@

\hypertarget{app:gui}{%
\subsection{Graphical User Interface}\label{app:gui}}

@@

\hypertarget{app:algo1}{%
\subsection{Coding Aggregation and Filtering}\label{app:algo1}}

@@

\hypertarget{app:intercoderagreement}{%
\subsection{Intercoder Agreement}\label{app:intercoderagreement}}

@@

\hypertarget{app:agreement_by_confidence}{%
\subsection{Intercoder Agreement by
Confidence}\label{app:agreement_by_confidence}}

@@

\hypertarget{recall}{%
\section{Recall}\label{recall}}

@@

\hypertarget{synthetic-narratives}{%
\subsection{Synthetic Narratives}\label{synthetic-narratives}}

@@

\hypertarget{synthetic-narrative-matches-cuban-missile}{%
\subsection{Synthetic Narrative Matches Cuban
Missile}\label{synthetic-narrative-matches-cuban-missile}}

@@

\hypertarget{synthetic-narrative-matches-crimea-donbas}{%
\subsection{Synthetic Narrative Matches
Crimea-Donbas}\label{synthetic-narrative-matches-crimea-donbas}}

@@

\hypertarget{precision}{%
\section{Precision}\label{precision}}

\hypertarget{crimea-donbas-narrative}{%
\subsection{Crimea-Donbas Narrative}\label{crimea-donbas-narrative}}

@@

\hypertarget{stratified-sentence-examples}{%
\subsection{Stratified Sentence
Examples}\label{stratified-sentence-examples}}

@@

\hphantom{em}
\begin{figure}[H]
\centering{\includegraphics[height=21cm]{"./ft_sample_precision_precision4.png"}}
\end{figure}

\hypertarget{cuban-missiles-crisis-maps}{%
\subsection{Cuban Missiles Crisis
Maps}\label{cuban-missiles-crisis-maps}}

\begin{figure}[H]
\caption{Crisis Map: Crimea-Donbas  \label{fig:p_471_icbe}}
\centering{\includegraphics[width=17cm]{./p_471_icbe.png}}
\end{figure}

@@

\hypertarget{crimea-donbas-crisis-maps}{%
\subsection{Crimea-Donbas Crisis Maps}\label{crimea-donbas-crisis-maps}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-reimersSentenceBERTSentenceEmbeddings2019}{}}%
Reimers, Nils, and Iryna Gurevych. 2019. {``Sentence-{BERT}: {Sentence
Embeddings} Using {Siamese BERT-Networks}.''} \emph{arXiv:1908.10084
{[}Cs{]}}, August. \url{https://arxiv.org/abs/1908.10084}.

\leavevmode\vadjust pre{\hypertarget{ref-reimersMakingMonolingualSentence2020}{}}%
---------. 2020. {``Making {Monolingual Sentence Embeddings
Multilingual} Using {Knowledge Distillation}.''} \emph{arXiv:2004.09813
{[}Cs{]}}, October. \url{https://arxiv.org/abs/2004.09813}.

\leavevmode\vadjust pre{\hypertarget{ref-shleiferPretrainedSummarizationDistillation2020}{}}%
Shleifer, Sam, and Alexander M. Rush. 2020. {``Pre-Trained
{Summarization Distillation}.''} \emph{arXiv:2010.13002 {[}Cs{]}},
October. \url{https://arxiv.org/abs/2010.13002}.
